Tulai

### 2023-10-03 paper/paper.qmd
add PCA test

>>>>

```{r}
# PCA test
# BM: new method to me! I found https://www.ncbi.nlm.nih.gov/pmc/articles/PMC8858582/

library(PCAtest)

# compute the tests and save the plot
jpeg( filename = here::here("figures/fig-pca-tests.jpg"),
      height  = 6, 
      width = 8,
      units = "in", 
      res = 900)

result <-
  PCAtest(pca_data,
          1000,
          1000,
          0.05,
          varcorr=FALSE,
          counter=FALSE,
          plot=TRUE)

dev.off()

knitr::include_graphics(here::here("figures/fig-pca-tests.jpg"))
